### 2019-02-27 paper/ms.tex
Add info about the specifics of interloper problem

Suppose we have a line $l$ which we are attempting to measure emission from at
some target redshift $z_t$. Then, the interloper problem is that at various other redshifts $z_i$ for $i=1,2,3,...$

>>>>

Suppose we have a line $l$ which we are attempting to measure emission from at
some target redshift $z_l$ and some observed frequency $\mynu{l}{o} =
\mynu{l}{e}/(1+z_l)$. Then, the interloper problem is that at various other
redshifts $z_i$ for $i=1,2,3,...$ there will be emission from lines with
emitted frequencies at redshift $z_i$ that satisfy the constraint $\mynu{l}{o}
= \mynu{i}{o}$, or equivalently,
\beq
\mynu{i}{e} = \mynu{l}{e}\frac{1+z_i}{1+z_l}\text{.}
\eeq
